---
title: "Assignment 9"
author: "PFL"
date: "2023-01-30"
output: html_document
---

### 1  
Using a for loop and an if statement, calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use print(counter) for the output.

```{r}
x<- rep(0:3, times=4)
x[1]

counter <- 0


for(i in 1:length(x)){
  if(x[i]==0){counter <- counter + 1}
}
print(counter)

```


### 2  
Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.

```{r}
m <- matrix(round(runif(20), digits = 2), nrow=5)

for(i in 1:nrow(m)) {
  for(j in 1:ncol(m)){
  m[i,j] <- i*j 
  }
}

print(m)
```


### 3  
Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}


```

